---
title: "Summary of progressive selection of variants Run1"
author: "Kiranmayee Bakshy"
date: "June 19, 2018"
output: html_document
---

**#A summary of the filtration_run1 is as follows**
 **Run1 consists of variants with no heterozygous genotype found in non-target animals**
 
  * Kept 3136979 out of 15440507 variant sites
  * Removed 1664776 singletons
  * Removed 342817 sites that were heterozygous in all other regions

 **Summary statistics for INFO fields** 
  
  ```{r}
plot_info<-readRDS("filtered_run1/filtered_run1.vcf.gz.rds")
summary(plot_info)
```

**Plink summary statistics such as MAF, AAF, fraction missing per sample, fraction missing per variant, HWE**
   
   ```{r}
#Summary of filtered dataset MAF
df<-readRDS("filtered_run1/filtered_run1.frq.rds")
dim(df)
summary(df)

#Summary of filtered dataset AAF
library(data.table)
df<-fread("filtered_run1/filtered_run1.afreq", header=T, select=c("ID", "ALT_FREQS"))
summary(df)

#Summary of filtered dataset fraction missing per variant
df<-readRDS("filtered_run1/filtered_run1.lmiss.rds")
summary(df)

#Summary of filtered dataset fraction missing per sample
df<-read.delim("filtered_run1/filtered_run1.imiss", header=T, sep="")
dim(df)
summary(df[,c(2,6)])
```